\hypertarget{ariaid-title1}{%
\section{Requirements}\label{ariaid-title1}}

\hypertarget{non-functional-requirements}{%
\subsection{Non-functional
requirements}\label{non-functional-requirements}}

\begin{enumerate}
\tightlist
\item
  The ontology should support multilingual content in at least English,
  French, German, Spanish and Italian languages.
\item
  The ontology must be based on the international, European or de-facto
  standards in existence or under development.
\item
  The ontology should be documented in an intuitive human friendly
  manner.
\end{enumerate}

\hypertarget{functional-requirements}{%
\subsection{Functional requirements}\label{functional-requirements}}

\begin{enumerate}
\tightlist
\item
  What is the a name legal document type? Draft communication, draft
  directive
\item
  What is the class notation/code if any is assigned? 5\_XC\_OJL,
  5\_PC\_EUR
\item
  What are the comments, examples, notes and other editorial remarks of
  a legal document class? Examples, change notes, history notes.
\item
  How is the class of legal documents defined? ... is a preparatory act
  of the commission which ...
\item
  How can be a legal document be classified using other existing
  classifications? resource-type:REG\_DRAFT, cdm:act\_preparatory
\item
  What are the hints for classifying a legal document? Keyword: "draft
  regulation", author: commission
\item
  To which groups document classes belong? Classification level 1/2/3
\item
  Which properties can be used to describe a legal document? Specific
  CDM properties
\item
  How is the property named ? Date of transposition, Date of signature
\item
  What is the formal path of the property? cdm:date\_transposition,
  cdm:resource\_legal\_date\_signature
\item
  What are the comments, examples, notes and other editorial remarks of
  a property describing legal document? Examples, change notes, history
  notes.
\item
  What constraints does the property have? Cardinality constraints,
  range constraints
\item
  What are the values of the constraints for a particular property on a
  particular class? min cardinality 0, max cardinality 1, value range
  restricted to FD 14 only,
\item
  How can the constraints be expressed in a human friendly manner? Human
  friendly text expressing the constraints all together generated using
  a string template.
\item
  What annotations does the property have?
  ann:comment\_on\_legal\_basis, ann:type\_of\_link\_target
\item
  What value restrictions does the annotation of a propriety has?
  at:fd\_370, at:subdivision
\item
  What value restrictions does the annotation of a specific property on
  a specific class? The annotation Comment on date of the property Date
  Document must be fd\_365:DATADOPT for the Draft regulation document
  type.
\item
  What is the property notation/code if any is assigned? ANN\_COD , AF,
  DP, LF
\item
  To which groups property belongs? Classification level 1/2
\end{enumerate}
